Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-01-02 paper.tex
review Research Problem (RP)

This position paper tackles five major problems in computer-aided verification for embedded systems, which are (partially) open in current published research.

@@

>>>>

This position paper tackles six major problems in computer-aided verification and synthesis for embedded systems, which are (partially) open in current published research.

@@

\textbf{(RP6)} develop automated synthesis approaches that are algorithmically and numerically sound, in order to handle control software that is tightly coupled with the physical environment by considering uncertain models and FWL effects.
